A common misapplication of statistical inference: nuisance control with null-hypothesis significance tests

### 2016-07-25 simulation/statfail.Rmd
better scope for "only"

## Generate graphics
```{r generate.graphics, dependson='simulate',cache=TRUE,message=FALSE,warning=FALSE}
# prettier names for the legend
results.long$type <-factor(results.long$type
                           ,levels=c("rejections"
                                     ,"manipulation_still_significant"
                                     ,"feature_has_no_effect"
                                     ,"feature_irrelevant_in_multiple"
                                     ,"not_rejected"
                                     ,"feature_relevant_in_multiple"
                                     ,"manipulation_only_in_simple")
                           ,labels = c("rejected"
                                       ,"but significant manipulation missed"
                                       ,"when feature was not significant in simple regression"
                                       ,"when feature was not significant in multiple regression"
                                       ,"accepted"
                                       ,"but feature still had an effect in multiple regression",
                                       "and the manipulation was only significant in simple regression"))

>>>>

## Generate graphics
```{r generate.graphics, dependson='simulate',cache=TRUE,message=FALSE,warning=FALSE}
# prettier names for the legend
results.long$type <-factor(results.long$type
                           ,levels=c("rejections"
                                     ,"manipulation_still_significant"
                                     ,"feature_has_no_effect"
                                     ,"feature_irrelevant_in_multiple"
                                     ,"not_rejected"
                                     ,"feature_relevant_in_multiple"
                                     ,"manipulation_only_in_simple")
                           ,labels = c("rejected"
                                       ,"but significant manipulation missed"
                                       ,"when feature was not significant in simple regression"
                                       ,"when feature was not significant in multiple regression"
                                       ,"accepted"
                                       ,"but feature still had an effect in multiple regression",
                                       "and the manipulation was significant only in simple regression"))
